Coherent optical association of a single molecule -- Supplemental material

### 2020-12-07 sm.tex
Regenerate PDF, whitespace
Update on Overleaf.

where $ \Delta $ is the single photon detuning and $ \Gamma_e $ is the excited state linewidth. The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $. In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $. These effective Rabi frequencies are used to calculate the Rabi frequency ratio and are the quantities reported in the main text when compared to experiment.

>>>>

where $ \Delta $ is the single photon detuning and $ \Gamma_e $ is the excited state linewidth. The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $. In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $. The effective Rabi frequencies for the $v' = 0$ state of $ c^3\Sigma^+_1$ and their ratio are reported in Table~\ref{tab:sm} at $3.75~\mathrm{mW}$ of tweezer power.

% $2\pi \times 15.3~\mathrm{kHz}$
% $ 2\pi \times 533~\mathrm{Hz}$
% $2\pi \times 573 ~\mathrm{MHz}$
% $2\pi \times 7.37 ~\mathrm{MHz}$

\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|} \hline
  $\Omega_m'$ &  $2\pi \times 573 ~\mathrm{MHz}$ \\
  $\Omega_a'$ &  $2\pi \times 7.37 ~\mathrm{MHz}$ \\
  $\Omega_m'/\Omega_a'$ & $ 78 $ \\ \hline
  \end{tabular}
  \caption{ The effective Rabi frequencies for the $v' = 0$ state of $c^3\Sigma^+_1$ at $ 3.75~\mathrm{mW}$ of tweezer power. 
    \label{tab:sm}}
\end{table}
